Interval Probability for Fuzzy Quantum Theories

### 2016-05-18 prob.tex
prob.tex \section{Quantum Probability Spaces} Starting "independent"...

\begin{definition}[Complement; Commutativity;
Independence~\cite{peres1995quantum,Griffiths2003}]~
\begin{itemize}
\item If $P$ is a projection operator, then $\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}P$
is also a projection operator, called complement. It is orthogonal to $P$, has
probability~$\mu\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}P\right)=1\tensor*[_{\mathbb{R}}]{-}{}\mu\left(P\right)$, 
and corresponds to the complement event~$\Omega\backslash E$
in classical probability.
\item Projection operators $P_{1}$ and $P_{2}$ commute if $P_{1}P_{2}=P_{2}P_{1}$.
The product of two projection operators~$P_{1}P_{2}$ is also a projection
operator if and only if they commute. This corresponds to the classical intersection
between event. Given a quantum probability measure $\mu$, two projections
$P_{1}$ and $P_{2}$ are independent if $P_{1}$ and $P_{2}$ commute
and $\mu\left(P_{1}P_{2}\right)=\mu\left(P_{1}\right)\mu\left(P_{2}\right)$.
\end{itemize}
\qed\end{definition}

>>>>

\begin{definition}[Complement; Commutativity~\cite{peres1995quantum,Griffiths2003}]~
\begin{itemize}
\item If $P$ is a projection operator, then $\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}P$
is also a projection operator, called complement. It is orthogonal to $P$, has
probability~$\mu\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}P\right)=1\tensor*[_{\mathbb{R}}]{-}{}\mu\left(P\right)$, 
and corresponds to the complement event~$\Omega\backslash E$
in classical probability.
\item Projection operators $P_{1}$ and $P_{2}$ commute if $P_{1}P_{2}=P_{2}P_{1}$.
The product of two projection operators~$P_{1}P_{2}$ is also a projection
operator if and only if they commute. This corresponds to the classical intersection
between events. 
\item \yutsung{The definition of independence is difference from difference
source:\\
1. In~\cite{Swart2013}, given two algebras~$\mathscr{B}_{1}$ and
$\mathscr{B}_{2}$ which commute with each other. They are \emph{logically
independent} if for all state~$\rho_{1}$ on $\mathscr{B}_{1}$ and
$\rho_{2}$ on $\mathscr{B}_{2}$, there is a unique state~$\rho$
on $\mathscr{B}_{1}\otimes\mathscr{B}_{2}$ such that $\rho\left(B_{1}\otimes B_{2}\right)=\rho_{1}\left(B_{1}\right)\rho_{2}\left(B_{2}\right)$
for all $B_{1}\in\mathscr{B}_{1}$ and $B_{2}\in\mathscr{B}_{2}$,
which denoted by $\rho_{1}\otimes\rho_{2}$. Notice that we require
$\mathscr{B}_{1}$ and $\mathscr{B}_{2}$ commute, and this definition
doesn't depend on a particular $\rho$. Then, logically independence
is used to defined the Bell inequality.\\
2. In~\cite{Yuan2012}, given a $\rho$ on an algebra~$\mathscr{C}$,
two sub-algebra $\mathscr{B}_{1}$ and $\mathscr{B}_{2}$ are independent
if $\rho\left(B_{1}B_{2}\right)=\rho\left(B_{1}\right)\rho\left(B_{2}\right)$
for all $B_{1}\in\mathscr{B}_{1}$ and $B_{2}\in\mathscr{B}_{2}$.
Notice that we doesn't require $\mathscr{B}_{1}$ and $\mathscr{B}_{2}$
commute, and this definition depend on a particular $\rho$.\\
3. In~\cite{GuehneKleinmannCabelloEtAl2010}, let $A$, $B$ be compatible
observables in a hidden variable model......................\\
}
\end{itemize}
\qed\end{definition}
